Treebeard : An Optimizing Compiler for Tree Based ML Inference

### 2022-04-14 docs/MICRO 2022/abstract.tex
Change title and add MLIR to abstract

  This paper presents Treebeard, an extensible compiler for decision tree models.
  TreeBeard progressively lowers inference code to LLVM through multiple intermediate 
  representations. By applying model specific optimizations at the higher levels, loop
  optimizations at the middle level and machine specific optimizations lower down,
  TreeBeard is able to specialize inference code for each model on each supported
  hardware target. Treebeard performs several novel optimizations such as tree tiling,
  tree walk unrolling and tree walk interleaving to improve performance of decision
  tree ensemble inference.

  We demonstrate the utility of Treebeard by evaluating it on a diverse set of
  tree ensemble models and comparing it against an unpotimized baseline. We report
  that Treebeard optimizations improve average latency over a batch of inputs by 2.2X.
  Further, we find that TreeBeard is significantly faster than other franeworks like
  XGBoost  (3X on average) and Treelite (5X on average) on both single and multi-core
  settings. 
\end{abstract}

>>>>

  This paper presents Treebeard, an extensible compiler for decision tree models.
  Treebeard progressively lowers inference code to LLVM IR through multiple intermediate
  representations. By applying model specific optimizations at the higher levels, loop
  optimizations at the middle level and machine specific optimizations lower down,
  Treebeard can specialize inference code for each model on each supported
  hardware target. Treebeard performs several novel optimizations such as tree tiling,
  tree walk unrolling and tree walk interleaving to improve performance of decision
  tree ensemble inference.

  We implement Treebeard using the MLIR compiler infrastructure and
  demonstrate the utility of Treebeard by evaluating it on a diverse set of
  tree ensemble models. We report that Treebeard optimizations improve
  average latency over a batch of inputs by 2.2X in comparison to an unoptimized baseline.
  Further, we find that Treebeard is significantly faster than other frameworks like
  XGBoost (3X on average) and Treelite (5X on average) in both single and multi-core
  settings.
\end{abstract}
